The Count Distinct Problem

### 2015-11-13 wim/paper.tex
flip flop
so many thing

Finally, running the algorithm tells us that the total number of unique application installs is \underline{RESULT GOES HERE}.\\

@@

\textit{Initialization} & \textit{Counting} & \textit{Implementing}

@@

Equation\ Goes\ Here.

@@

Results\ From\ Plugging\ In\ 200,000,000,
which means that we will have roughly \underline{INSERT RESULT HERE} unique hashtags by the HyperLogLog algorithm.\\ 
%%%%%%%%RESULTS GO HERE%%%%%%%%%%

>>>>

Finally, running the algorithm tells us that the total number of unique application installs is 3216.\\

@@

Initialization & Counting & Implementing

@@

f(x) = 0.284356 x + 7,361.39.

@@

f(200,000,000) &= 0.284356(200,000,000) + 7,361.39\\
&= 56,878,500,
which means that we will have roughly 56 million unique hashtags by the HyperLogLog algorithm.\\ 

### 2015-11-13 wim/presentation.tex
so many thing

\section{The HyperLogLog}
\begin{frame}{The Algorithm}
\begin{enumerate}
\pause
\item Create a 
\end{enumerate}
\end{frame}
\end{document}

>>>>

\section{The HyperLogLog}
\begin{frame}{The Algorithm}
\begin{enumerate}
\pause
\item Create a bitmap in memory. We will call this $\mathbb{V}$.
\pause
\item For each value $s$ is $\mathbb{S}$, hash $s$ to a binary number.
\pause
%\item
\begin{itemize}
\item We will use a \textit{Murmur Hash} to do this.
\end{itemize}
\pause
\item Analyze the first sequence of 0's in the binary value, and store the number of leading 0's into the bitmap.
\begin{itemize}
\item If the sequence of 0's has been seen before, there is a high probability that the term is a duplicate
\end{itemize}
\pause
\item Take the harmonic average of all the totals in the bitmap.
\end{enumerate}
\end{frame}

\begin{frame}{The Math}
\pause
\begin{itemize}
\item How much memory is required?
\pause
\[
\text{Memory Required} = \log_{2}{(\log_{2}{(M)})}
\]
\pause
\item $M$ is the size of the original set of data ($\mathbb{S}$).
\pause
\item What is the predicted error?
\pause
\[
\text{Error} = \frac{\sqrt{3\log{(2)} - 1}}{m}
\]
\pause
\item $m$ is the number of spaces in the bitmap ($\mathbb{V}$).
\end{itemize}
\end{frame}

\begin{frame}{Solving the Twitter Problem}
\pause
\begin{itemize}
\item How can we process count 200,000,000 hashtags on an average computer?
\pause
\item We can lower the sample size and apply a best fit line to the data.
\begin{enumerate}
\pause
\item For 24 hours, gather 2000 tweets containing ``\#'' every 2 minutes.
\pause
\item Using the HyperLogLog, determine the unique number of total hashtags every time a new sample is gathered.
\end{enumerate}
\end{itemize}
\end{frame}

\begin{frame}{Results}
\pause
\begin{figure}
\includegraphics[scale=0.5]{twitter_problem/resultspng}
\caption{$0.284356 x + 7361.39$}
\end{figure}
\pause
\begin{itemize}
\item Plugging in 200,000,000 gives us
\pause
\item $5.68785\times10^7$ unique hashtags.
\end{itemize}
\end{frame}
\end{document}
